---
title: "Homework 1"
author: "Pei Yang Hsieh"
date: 2018-09-16
output: github_document
---

```{r setup, include = FALSE}
library(tidyverse)
```

The purpose of this file is to complete Homework 1

# Problem 1

------------------------------------------------------------

## Create a dataframe containing variables of four different types.

*   A random sample of size 10 from a uniform[0, 5] distribution

*   A logical vector indicating whether elements of the sample are greater than 2

*   A (length-10) character vector

*   A (length-10) factor vector


```{r example_df}

set.seed(1234)
samp = runif(10, min = 0, max = 5)

example_df = tibble(
  vec_numeric = samp,
  vec_logical = samp > 2,
  vec_char = c("This", "Is", "A", "Character", "Vector", "For", "Homework", "One", "Data", "Science"),
  vec_factor = factor(c("male", "male", "female", "female", "male", "male", "female", "female", "male", "male"))
)
```

## Take the mean of each variable in dataframe. 

```{r mean}

mean(example_df$vec_numeric)
mean(example_df$vec_logical)
mean(example_df$vec_char)
mean(example_df$vec_factor)
```

Taking the mean only works for numeric and logical vectors, not character and factor vectors. Character and factor vectors cannot be recognized as numbers.

## Use as.numeric on logical, character, and factor variables. 

```{r apply_as.numeric, eval = FALSE}

as.numeric(example_df$vec_logical)
as.numeric(example_df$vec_char)
as.numeric(example_df$vec_factor)
```

For logical variables, it changes the T/F into 1's and 0's. For character variables, it becomes NA. For factor variables, it becomes 1's and 2's.

# Problem 2

------------------------------------------------------------

## Create a dataframe of:

*   x: a random sample of size 1000 from a standard Normal distribution

*   y: a random sample of size 1000 from a standard Normal distribution

*   A logical vector indicating whether the x + y > 0 

*   A numeric vector created by coercing the above logical vector

*   A factor vector created by coercing the above logical vector

```{r df_normal}

set.seed(4321)
x_1000 = rnorm(1000)
y_1000 = rnorm(1000)

df_normal = tibble(
  x = x_1000,
  y = y_1000,
  logical_xy = x + y > 0,
  numeric_xy = as.numeric(logical_xy),
  factor_xy = as.factor(logical_xy)
)
```
